Single Cell Xenopus TMT Analysis

### 2020-03-11 Manuscript/Manuscript.Rmd
.

@@

```{r figure_4, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE, eval=TRUE, fig.cap=fig_legend_3}
library(circlize)

@@

bottom <- p2 + p3 + plot_layout(widths = c(1,2))
(p1 + plot_spacer()) / bottom + 
  plot_annotation(tag_levels = "A")

fig_legend_3 <- c("A) A representative heat-map of one of the low normalized variation groups with high levels of correlated proteins (Large ribosomal subunit). B) A simple model showing the percent of potentially assembled subunits of an idealized heteromeric 10 subunit complex. Both the variation of expression between the subunits as well as the coordinated expression between them can effect the percent of maximum assembled complexes. C) Heat-map showing the total variance as a function of coefficient of variation and correlation from the idealized model in B).")
```

>>>>

\newpage

@@

\newpage

```{r figure_4, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE, eval=TRUE, fig.cap=fig_legend_4}
library(circlize)

@@

p4 <- cowplot::ggdraw() + cowplot::draw_image(magick::image_read_svg("../images/complex_cartoon.svg"))

bottom <- p2 + p3 + plot_layout(widths = c(1,2))
(p1 + p4) / bottom + 
  plot_annotation(tag_levels = "A")

fig_legend_4 <- c("A) A representative heat-map of one of the low normalized variation groups with high levels of correlated proteins (Large ribosomal subunit). B) A simple model showing the percent of potentially assembled subunits of an idealized heteromeric 10 subunit complex. Both the variation of expression between the subunits as well as the coordinated expression between them can effect the percent of maximum assembled complexes. C) Heat-map showing the total variance as a function of coefficient of variation and correlation from the idealized model in B).")
```

\newpage

### 2020-03-11 Untitled.Rmd
.

cor_rug_plot <- function(x){
  temp <- filter(allGO, GOterms %in% x) %>%
    dplyr::select(GO, cors) %>% unnest(cols = cors)

  temp <- allGO %>% select(GO, cors) %>%
    unnest(cols = cors) %>% mutate(GO = "all") %>%
    rbind(temp,.)

  ggplot(temp, aes(x = cors, fill = GO, color = GO)) +
    geom_density(alpha = 0.25) + 
    geom_rug(data = filter(temp, GO != "all")) + 
    theme_bw()
}

>>>>

cor_rug_plot <- function(x){
  temp <- filter(allGroups, accession %in% x) %>%
    dplyr::select(name, cors) %>% unnest(cols = cors)

  temp <- allGroups %>% select(name, cors) %>%
    unnest(cols = cors) %>% mutate(name = "all") %>%
    rbind(temp,.)

  ggplot(temp, aes(x = cors, fill = name, color = name)) +
    geom_density(alpha = 0.25) + 
    geom_rug(data = filter(temp, name != "all")) + 
    theme_bw()
}
cor_rug_plot("GO:0006739")
```
